PANCHANGE_data_preprocessing

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added data groups chunk - may need revisions

```{r pre, base, retro comparison for phq, pcl and gad}
#see Issue for more details here
```

```{r data level groups}

@@

>>>>

@@

#Total score comparison between PHQ, PCL and GAD
```{r pre, base, retro comparison for phq, pcl and gad}
#see Issue for more details here
```

#Data level groups
Identify which data (prepan, retro and baseline) each participant has
Has only prepandemic == 0
prepandemic and baseline == 1
prepandemic, baseline, and retrospective == 2
++KT: not sure how best to categorise here so this may need some revision. 
```{r data level groups}
dat.glad <- dat.glad %>%
  mutate(
    data_group_full_numeric =
      case_when(
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4,
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3,
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PCL-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_full = 
      recode_factor(
        data_group_full_numeric,
        "0" = "Only prepandemic data",
        "1" = "Prepandemic and baseline data",
        "2" = "Prepandemic, baseline and retrospective PHQ data",
        "3" = "Prepandemic, baseline and retrospective GAD data",
        "4" = "Prepandemic, baseline and retrospective PCL data",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat.glad$data_group_full)
```

```{r}
rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at prepanline
           %in%
             pcl.items_prepan]
```
